---
engine: knitr
format: live-html
webr:
  packages:
  - ggplot2
  - datasauRus

title: "Lecture 1"
filters:
  - naquiz
---

{{< include ./_extensions/r-wasm/live/_knitr.qmd >}}

::: callout-tip
Lecture 1 exercises using naquiz/nareal
:::

```{r set_up}
library(tidyverse)
library(data.table)
library(patchwork)
library(kableExtra)
```

## Power of visualization

You are provided with a table summarising several datasets. Look at the summary statistics carefully and answer the questions below based on your interpretation of the data.

```{r}

library(datasauRus)
data(datasaurus_dozen)
dat <- datasaurus_dozen
setDT(dat)


dat[, {
  x_mean  <- mean(x)
  x_sd <- sd(x)
  y_mean <- mean(y)
  y_sd <- sd(y)
  corr <- cor(x, y)
  list(x_mean, x_sd,
  y_mean, y_sd, corr)
}, by = "dataset"] |>
  
  kbl()

```

#### Question 1

::: question
Since the datasets have nearly identical means, standard deviations, and correlations, what can you infer about the spread of points?

::: choices
::: choice
All datasets will likely have identical visual patterns
:::

::: choice
The datasets may have similar visual spreads but differ in shape
:::

::: {.choice .correct-choice}
None, no conclusions about the distribution of the points can be made
:::
:::
:::

#### Question 2

The different datasets have identical means, standard deviations, and correlations, is it safe to conclude that the spread of points to look similar in all cases? Why or why not?/ Is it possible for datasets to have identical summary statistics yet represent fundamentally different underlying distributions?

*TO ADD: Question Answers*

Run the following code to visualize the dino dataset.

```{webr}
    #| exercise: ex_2
    dat <- datasaurus_dozen

    ggplot(data = subset(dat, dataset == "dino"),
           mapping = aes(x = x,
                         y = y)) +
        geom_point() 
```

#### Question 3

Have your conclusions changed based on the visualization?

::: {.callout-caution collapse="true"}
## All datasets visualised

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, colour = dataset))+
    geom_point()+
    theme(legend.position = "none")+
    facet_wrap(~dataset)
  
```
:::

## Visual channels

::: {#fig-palmerpenguins}
```{r}
library(palmerpenguins)

ggplot(data = penguins, 
       mapping = aes(x = flipper_length_mm, y = bill_length_mm)) +
  geom_point(
    aes(color = species, shape = species),
    size = 2, 
    alpha = 0.8 
  ) +
  
  scale_color_manual(
    values = c("orange", 
               "purple3", 
               "seagreen")
  )


```
:::

::: question
#### In @fig-palmerpenguins which channel(s) are used to depict species?

::: choices
::: choice
Horizontal (x-axis) position of the mark
:::

::: choice
Vertical (y-axis) position of the mark
:::

::: {.choice .correct-choice}
Colour
:::

::: {.choice .correct-choice}
Shape
:::

::: choice
Opacity
:::
:::
:::

::: question
#### In @fig-palmerpenguins which channel(s) are used to depict flipper length?

::: choices
::: {.choice .correct-choice}
Horizontal (x-axis) position of the mark
:::

::: choice
Vertical (y-axis) position of the mark
:::

::: choice
Colour
:::

::: choice
Shape
:::

::: choice
Opacity
:::
:::
:::

::: question
#### Using multiple visual channels to represent the same variable is known as:

::: choices
::: {.choice .correct-choice}
Redundant coding
:::

::: choice
Dimensionality reduction
:::
:::
:::

::: {#fig-palmerpenguins2}
```{r}
#| fig-cap-location: top

ggplot(data = penguins, 
       mapping = aes(x = flipper_length_mm, 
                     y = bill_length_mm, 
                     colour = island,
                     size = body_mass_g)) +
  geom_point(alpha = 0.8) 
  
```
:::

::: question
#### Which of the following is correct for @fig-palmerpenguins2?

::: choices
::: choice
The size and colour of the marks represent body mass (g) and species, respectively.
:::

::: {.choice .correct-choice}
The size and colour of the marks represent body mass (g) and island, respectively.
:::
:::
:::
